A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-24 nips2015.tex
affiliation

\documentclass[envcountsame]{llcns2e/llncs}
\usepackage{url}
%\usepackage{times}
\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage[FIGTOPCAP]{subfigure}

\newtheorem{fact}{Fact}
\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\proj}{proj}
\DeclareMathOperator{\prox}{prox}

\title{\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate
  Nash equilibria in two-person zero-sum games with imcomplete
  information}
\author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
\institute{
Parietal team, Inria Saclay Ile-de-France, Saclay, France
}

@@

\subsection{Notation and terminology}
\paragraph{\textbf{General notions.}}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0),
max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

@@

where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') < +\infty$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $-\infty \le \phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
Thus, one can compute the primal-dual gap between the primal LCP
\eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.
\qed

@@

Algorithm \ref{Tab:algo} is then obtained from \cite[Algorithm
  T-BD]{he2013accelerating}, applied on the GSP
\eqref{eq:unconstrained_pb} with the choice of parameters: $\sigma = 1
\in (0, 1]$, $\sigma_x = \sigma_y = 0 \in [0, \sigma)$,
    $\lambda_{xy} := \frac{1}{\sigma L_{xy}}\sqrt{(\sigma^2 -
        \sigma_x^2)(\sigma^2 - \sigma_y^2)} = \sigma / \|K\| =
      1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
      \lambda_{xy}]$. The convergence result follows immediately from
  \cite[Theorem 4.2]{he2013accelerating}.
  \qed
\end{proof}

@@

\begin{eqnarray*}
  \begin{split}
    E_2y^* - e_2 = [&-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29
      \times 10^{-6}, -1.50 \times 10^{-6},\\
      &2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
      10^{-7}]^T
    \end{split}
\end{eqnarray*}
Finally, one checks that
\begin{eqnarray*}
  {x^*}^TAy^* = \textbf{-0.05555},
\end{eqnarray*}
 which agrees to 5 d.p with the value of $-1 / 18$ computed
 analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
 evolution of the dual gap and the expected value of the game across
 iterations is shown in Figure \ref{Tab:dgap_curve}.

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e}
%\documentclass[envcountsame]{llcns2e/llncs}
\usepackage{url}
\usepackage{times}
\usepackage{amsmath,amsfonts, amsthm}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage[FIGTOPCAP]{subfigure}

\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}

\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}{Remark}
\newtheorem{fact}{Fact}

\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\proj}{proj}
\DeclareMathOperator{\prox}{prox}

\title{
  %\hrule\hrule\bigskip\bigskip
  A simple and efficient algorithm for computing approximate
  Nash equilibria in two-person zero-sum games with imcomplete
  information}
\author{Elvis DOHMATOB
\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
\\\texttt{firstname.lastname@inria.fr}
}

@@

\subsection{Notation and terminology}
\paragraph{\textbf{General notions.}}
Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
of all subsets of $X$, or equivalently the set of all binary
functions on $X$.

Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0),
max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.

Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

@@

where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') < +\infty$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $-\infty \le \phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
Thus, one can compute the primal-dual gap between the primal LCP
\eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.

@@

Algorithm \ref{Tab:algo} is then obtained from \cite[Algorithm
  T-BD]{he2013accelerating}, applied on the GSP
\eqref{eq:unconstrained_pb} with the choice of parameters: $\sigma = 1
\in (0, 1]$, $\sigma_x = \sigma_y = 0 \in [0, \sigma)$,
    $\lambda_{xy} := \frac{1}{\sigma L_{xy}}\sqrt{(\sigma^2 -
        \sigma_x^2)(\sigma^2 - \sigma_y^2)} = \sigma / \|K\| =
      1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
      \lambda_{xy}]$. The convergence result follows immediately from
  \cite[Theorem 4.2]{he2013accelerating}.
\end{proof}

@@

\begin{eqnarray*}
  \begin{split}
    E_2y^* - e_2 = [&-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29
      \times 10^{-6}, -1.50 \times 10^{-6},\\
      &2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
      10^{-7}]^T
    \end{split}
\end{eqnarray*}
Finally, one checks that
\begin{eqnarray*}
  {x^*}^TAy^* = \textbf{-0.05555},
\end{eqnarray*}
 which agrees to 5 d.p with the value of $-1 / 18$ computed
 analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
 evolution of the dual gap and the expected value of the game across
 iterations are shown in Figure \ref{Tab:dgap_curve}.
